% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}

% allows for temporary adjustment of side margins
\usepackage{chngpage}

% just makes the table prettier (see \toprule, \bottomrule, etc. commands below)
\usepackage{booktabs}

\usepackage[utf8]{inputenc}
%\usepackage[font=small,skip=0pt]{caption}

% footnotes
\usepackage{scrextend}

% colors
\usepackage[usenames, dvipsnames]{color}

% underline
\usepackage{tikz}
\newcommand{\udensdot}[1]{%
    \tikz[baseline=(todotted.base)]{
        \node[inner sep=1pt,outer sep=0pt] (todotted) {#1};
        \draw[densely dotted] (todotted.south west) -- (todotted.south east);
    }%
}%

\newcommand{\uloosdot}[1]{%
    \tikz[baseline=(todotted.base)]{
        \node[inner sep=1pt,outer sep=0pt] (todotted) {#1};
        \draw[loosely dotted] (todotted.south west) -- (todotted.south east);
    }%
}%

\newcommand{\udash}[1]{%
    \tikz[baseline=(todotted.base)]{
        \node[inner sep=1pt,outer sep=0pt] (todotted) {#1};
        \draw[dashed] (todotted.south west) -- (todotted.south east);
    }%
}%

\newcommand{\udensdash}[1]{%
    \tikz[baseline=(todotted.base)]{
        \node[inner sep=1pt,outer sep=0pt] (todotted) {#1};
        \draw[densely dashed] (todotted.south west) -- (todotted.south east);
    }%
}%

\newcommand{\uloosdash}[1]{%
    \tikz[baseline=(todotted.base)]{
        \node[inner sep=1pt,outer sep=0pt] (todotted) {#1};
        \draw[loosely dashed] (todotted.south west) -- (todotted.south east);
    }%
}%

% URL handling
\usepackage{url}
\urlstyle{same}

%\usepackage{makeidx}  % allows for indexgeneration

%\usepackage{amsmath}
\usepackage{amsmath, amssymb}
\usepackage{mathabx}
\usepackage{caption} 
\captionsetup[table]{skip=10pt}

% monospace within text
\newcommand{\ms}[1]{\texttt{#1}}

% examples
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{ex}{Verbatim}{numbers=left,numbersep=2mm,frame=single,fontsize=\scriptsize}

\usepackage{xspace}
% Einfache und doppelte Anfuehrungszeichen
\newcommand{\qs}{``} 
\newcommand{\qe}{''\xspace} 
\newcommand{\sqs}{`} 
\newcommand{\sqe}{'\xspace} 

% checkmark
\usepackage{tikz}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;} 

% Xs
\usepackage{pifont}

% Tabellenabstände kleiner
\setlength{\intextsep}{10pt} % Vertical space above & below [h] floats
\setlength{\textfloatsep}{10pt} % Vertical space below (above) [t] ([b]) floats
% \setlength{\abovecaptionskip}{0pt}
% \setlength{\belowcaptionskip}{0pt}

\usepackage{tabularx}
\newcommand{\hr}{\hline\noalign{\smallskip}} % für die horizontalen linien in tabellen

% Todos
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
\newcommand{\er}[1]{\todo[size=\small, color=red!40]{\textbf{Erman:} #1}}
\newcommand{\an}[1]{\todo[size=\small, color=blue!40]{\textbf{Andy:} #1}}

\newenvironment{table-1cols}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l}
  \hline
  \textbf{Requirements} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{table-2cols}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l|l}
  \hline
  \textbf{Requirements} & \textbf{Covering DSCLs} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{complexity}{
  %\scriptsize
  %\sffamily
  %\vspace{0.3cm}
  \begin{tabular}{l|l}
  \hline
  \textbf{Complexity Class} & \textbf{Complexity} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{DL}{
  %\scriptsize
  %\sffamily
  \vspace{0cm}
  \begin{tabular}{r l}

}{
  \end{tabular}
  %\linebreak
}


\newenvironment{evaluation}{
  %\scriptsize
  %\sffamily
  %\vspace{0.3cm}
  \begin{tabular}{l|c|c|c|c|c|c}
  \hline
  \textbf{Constraint Class} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{constraint-languages-complexity}{
  %\scriptsize
  %\sffamily
  %\vspace{0.3cm}
  \begin{tabular}{l|c|c|c|c|c|c}
  \hline
  \textbf{Complexity Class} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{user-fiendliness}{
  %\scriptsize
  %\sffamily
  %\vspace{0.3cm}
  \begin{tabular}{l|c|c|c|c|c}
  \hline
  \textbf{criterion} & \textbf{DSP} & \textbf{OWL2} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\setcounter{secnumdepth}{5}

% tables
\usepackage{array,graphicx}
\usepackage{booktabs}
\usepackage{pifont}
\newcommand*\rot{\rotatebox{90}}
\newcommand*\OK{\ding{51}}
\usepackage{booktabs}
\newcommand*\ON[0]{$\surd$}

\usepackage{tablefootnote}

\usepackage{float}

\begin{document}
\renewcommand{\arraystretch}{1.3}
%
%
\title{An Evaluation \\
of Metadata and Data Quality}
\subtitle{on Person-Level, Aggregated, Thesauri, Statistical Classifications, and Rectangular Data Sets}

%\title{An Evaluation}
%\subtitle{of the Quality of Metadata on Person-Level, Aggregated, Thesauri, and Statistical Classifications Data Sets and of the Quality of Rectangular Data}

\titlerunning{XXXXX}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Thomas Bosch\inst{1} \and Benjamin Zapilko\inst{1} \and Joachim Wackerow\inst{1} \and Kai Eckert\inst{2}}
%
\authorrunning{} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
\email{\{firstname.lastname\}@gesis.org},\\ 
\and
University of Mannheim, Germany \\
\email{kai@informatik.uni-mannheim.de} 
}

\maketitle              % typeset the title of the contribution

\begin{abstract}
From 2012 to 2015 together with other Linked Data community members and experts from the social, behavioural, and economic sciences (\emph{SBE}), we developed diverse vocabularies to represent \emph{SBE} metadata and rectangular data in RDF.
The \emph{DDI-RDF Discovery Vocabulary (Disco)} 
is designed to support the dissemination, management,
and reuse of person-level data, i.e., data about individuals, households, and businesses, collected in form of responses to studies and archived for research purposes.
The \emph{RDF Data Cube Vocabulary (Data Cube)} is a W3C recommendation for expressing \emph{data cubes}, i.e. multi-dimensional aggregate data. 
\emph{Physical Data Description (PHDD)} is a vocabulary to model data in rectangular format. 
The data could either be represented in records with character-separated values (\emph{CSV}) or fixed length. 
The \emph{Simple Knowledge Organization System (SKOS)} is a vocabulary to build knowledge organization systems such as thesauri, classification schemes, and taxonomies.
\emph{XKOS} is a SKOS extension to describe formal statistical classifications. 

To ensure high quality of and trust in both metadata and data, their representation in RDF must satisfy certain criteria - specified in terms of RDF constraints.
In this paper, we evaluated the metadata and data quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), thesauri (\emph{SKOS}), rectangular (\emph{PHDD}), and statistical classification (\emph{XKOS}) data sets by means of RDF constraints.
RDF Constraints are instances of RDF constraint types either corresponding to RDF validation requirements or to data model specific constraint types.
We validated more than 4.2 billion triples and 15 thousand data sets
using the \emph{RDF Validator}, a validation environment which is available at \url{http://purl.org/net/rdfval-demo}.

\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, Thesauri, SKOS, Rectangular Data, Statistical Classifications, XKOS, Linked Data, Semantic Web}
\end{abstract}

\section{RDF Validation of Metadata and Data}
\label{rdf-validation}

Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each (represented by different constraint languages).
The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
Therefore, this technical report contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
We recently published a technical report in which we describe constraints to validate metadata on person-level, aggregated data, and thesauri.
We assign each constraint to constraint types corresponding to RDF validation requirements or to data model specific constraint types\footnote{Requirements/Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-1}}
\cite{BoschZapilkoWackerowEckert2015}.

We distinguish two validation types:
(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of given data models.
(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges.
We determined the default \emph{severity level} (corresponds to requirement \emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ (informational) via $\mathcal{SL}_{1}$ (warning) to $\mathcal{SL}_{2}$ (error). 
Although we provide default severity levels for each constraint, users should be able to specify severity levels of constraints they need to validate for their individual use cases, i.e., users should be able to define use case specific severity levels for constraints.

\section{Evaluation}

We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of both $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
We validated 
9,990 / 3,775,983,610 (\emph{QB}),
4,178 / 477,737,281 (\emph{SKOS}), and 
1,526 / 9,673,055 (\emph{Disco}) data sets / triples using the \emph{RDF Validator}\footnote{For details about the \emph{RDF Validator} see \cite{BoschEckert2014-2}} (available at \url{http://purl.org/net/rdfval-demo}) in batch mode.
That are more than 4.2 billion triples and 15 thousand data sets.
We validated, i.a., 
(1) \emph{QB} data sets published by the \emph{Australian Bureau of Statistics (ABS)},
the \emph{European Central Bank (ECB)}, and the
\emph{Organisation for Economic Co-operation and Development (OECD)},
(2) \emph{SKOS} thesauri like the \emph{AGROVOC Multilingual agricultural thesaurus},
the \emph{STW Thesaurus for Economics}, and the
\emph{Thesaurus for the Social Sciences (TheSoz)}, and
(3) \emph{Disco} data sets provided by the \emph{Microdata Information System (Missy)}, 
the \emph{DwB Discovery Portal}, the
\emph{Danish Data Archive (DDA)}, and the
\emph{Swedish National Data Service (SND)}.
As we evaluated nearly 10 thousand \emph{QB} data sets, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
The correctness of all constraints, i.e., the gold standard, has been proved by SBE domain experts.
Table \ref{tab:evaluation} shows the evaluation results.

\begin{table}[H]
		\scriptsize
    \begin{center}
    \begin{tabular}{@{}lcccc@{}}
%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
%    \\  \cmidrule{2-7}
    \\       \textbf{Criteria\tablefootnote{\emph{C (constraints), CT (constraint types), CV (constraint violations)}}}
           & \textbf{\emph{Disco}}
           & \textbf{\emph{QB}}
					 & \textbf{\emph{SKOS}}
					 & \textbf{Total}
    \\ \midrule
		\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
		\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
		\hline
    \emph{CV} & 3,545,703 & 45,635,846 & 5,540,988 & 54,722,537\\
		\emph{CV ($\mathcal{SL}_{0}$)} & 2,437,922 (68.8\%) & 0 (0\%) & 2,281,740 (41.2\%) & 4,719,662 (8.6\%) \\
		\emph{CV ($\mathcal{SL}_{1}$)} & 473,574 (13.4\%) & 45,520,613 (99.75\%) & 3,259,248 (58.8\%) & 49,253,435 (90\%) \\
    \emph{CV ($\mathcal{SL}_{2}$)} & 634,207 (17.9\%) & 115,233 (0.25\%) & 0 (0\%) & 749,440 (1.4\%) \\
		\hline
		\emph{CT} & 52 (15\textbar 37)\tablefootnote{(\label{fnt:1}implemented \textbar not yet implemented)} & 20 (7\textbar 13) & 14 (4\textbar 10) & 53 \\
		\emph{CT} ($\mathcal{C}_{C}$) & 30 (57.7\%) & 5 (25\%) & 5 (35.7\%) & 30 (56.6\%) \\
		\emph{CT} ($\mathcal{C}_{T}$) & 22 (42.3\%) & 15 (75\%) & 9 (64.3\%) & 23 (43.4\%) \\
		\hline
		\emph{C} & 142 (77\textbar 65) & 35 (20\textbar 15) & 35 (17\textbar 18) & 212 \\
		\emph{C} ($\mathcal{C}_{C}$) & 72 (50.7\%) & 16 (45.7\%\textbar12\textbar4) & 21 (60\%\textbar13\textbar8) & 109 (51.4\%) \\
		\emph{C} ($\mathcal{C}_{T}$) & 70 (49.3\%) & 19 (54.3\%\textbar8\textbar11) & 14 (40\%\textbar4\textbar10) & 103 (48.6\%) \\
		\emph{C ($\mathcal{SL}_{0}$)} & 75 (52.8\%\textbar44\textbar31)& 4 (11.4\%\textbar0\textbar4) & 21 (60\%\textbar12\textbar9) & 100 (47.2\%) \\
		\emph{C ($\mathcal{SL}_{1}$)} & 9 (6.3\%\textbar8\textbar1)& 3 (8.6\%\textbar3\textbar0) & 5 (14.3\%\textbar5\textbar0) & 17 (8\%) \\
		\emph{C ($\mathcal{SL}_{2}$)} & 58 (40.8\%\textbar25\textbar33) & 28 (80\%\textbar17\textbar11) & 9 (25.7\%\textbar0\textbar9) & 95 (44.8\%) \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation}
		\label{tab:evaluation}
    \end{center}
\end{table}

We identified 142 \emph{Disco} constraints ($\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints to the same extend) assigned to 52 distinct constraint types and implemented 77 of them to actually validate person-level data sets.  
For \emph{QB}, we specified more $\mathcal{C}_{T}$ (54\%) than $\mathcal{C}_{C}$ constraints; for \emph{SKOS}, however, more $\mathcal{C}_{C}$ constraints (60\%).
We instantiated more $\mathcal{C}_{C}$ (58\%) than $\mathcal{C}_{T}$ constraint types to define \emph{Disco} constraints; 
for \emph{QB} (75\%) and \emph{SKOS} (64\%), on the other side, more $\mathcal{C}_{T}$ constraint types. 
In total, we used 53 of overall 82 distinct constraint types (57\% of them are $\mathcal{C}_{C}$ constraint types) to define 212 constraints (equally $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints).

For \emph{Disco} and \emph{SKOS}, more than the half of the constraints are associated with the weakest severity level $\mathcal{SL}_{0}$.
Within the context of \emph{QB}, 80\% of the constraints are classified as the most serious ones ($\mathcal{SL}_{2}$).
All in all, there are a little bit more $\mathcal{SL}_{0}$ then $\mathcal{SL}_{2}$ constraints, whereas $\mathcal{SL}_{1}$ constraints are negligible.
\emph{Existential quantifications} (32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
By validating \emph{QB} data sets, we got the most constraint violations (more than 45 millions), followed by \emph{SKOS} and \emph{Disco} (with more than 5.5 and 3.5 millions) - consequently, almost 55 million constraint violations were raised during the evaluation which could be used to enhance the metadata quality of these data sets.  
Close to 70\% of all \emph{Disco} constraint violations are caused by violating $\mathcal{SL}_{0}$ constraints.
For \emph{QB} (nearly 100\%) and \emph{SKOS} (almost 60\%), the majority of the raised constraint violations are classified to be more serious ($\mathcal{SL}_{1}$).
80\% of all \emph{QB} constraints are $\mathcal{SL}_{2}$ constraints leading to less than 1\% of all \emph{QB} constraint violations.
Altogether, exactly 90\% of the constraint violations are assigned to the severity level $\mathcal{SL}_{1}$.
These findings are surprising as only 8\% of all defined constraints are $\mathcal{SL}_{1}$ constraints.
The constraints responsible for the largest numbers of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916) (\emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102) (\emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903) (\emph{SKOS}).

\subsection{Legend}

In this section, we describe how the tables in this paper should be read.
Table \ref{tab:legend} gives an overview over the symbols used in subsequent tables.

\begin{table}
	\centering
		\begin{tabular}{c|l}
      \textbf{Symbol} & \textbf{Description} \\	
			\hline
			\textbf{$\checkmark$} & Validation Successful (without any constraint violation) \\
			\textbf{\emph{X}} & Constraint Violations \\
			\hline
			\textbf{\textgreater \emph{X}} & Poor Performance/Scaling \\
      \ding{55} & Very Poor Performance/Scaling \\
			\hline
			\textbf{\emph{(!)}} & Not Yet Implemented Constraint \\
			\hline
			\textbf{\emph{(X)}} & The validation of \emph{X} data sets could not be finished, \\
			           & due to SPARQL endpoints' technical restrictions (e.g. defined timeouts). \\
			\hline
			\textbf{\emph{\textsuperscript{*}}} & default severity level $\mathcal{SL}_{0}$ (informational) \\
			\textbf{\emph{\textsuperscript{**}}} & default severity level $\mathcal{SL}_{1}$ (warning) \\
			\textbf{\emph{\textsuperscript{***}}} & default severity level $\mathcal{SL}_{2}$ (error) \\
		\end{tabular}
	\caption{Legend}
	\label{tab:legend}
\end{table}

\begin{itemize}
	\item \textbf{Constraint Violations.}
When constraints are violated, 
\emph{X} indicates the number of raised constraint violation triples. 

  \item
\textbf{Poor Performance/Scaling.}
The performance of the implementation of the underlying SPARQL CONSTRUCT query 
is too poor to get all resulting constraint violation triples. 
Therefore, a limit of \emph{X} result constraint violation triples is set. 
It is likely that there are more than \emph{X} constraint violations.
Although, the result set contains not the whole set of raised constraint violation triples,
the constraint can be used as an indicator if there is data not conforming to the constraint and
to resolve constraint violations step by step. 
As part of future work, the performance will be improved.

  \item
\textbf{Very Poor Performance/Scaling.} 
The performance of the implementation of the underlying SPARQL CONSTRUCT query 
is too poor to get any results, even though a limit of result constraint violation triples is set. 
As part of future work, the performance will be improved. 
\end{itemize}

\section{Evaluation of Person-Level Metadata (\emph{Disco})}

In this section, the quality of the metadata on person-level (\emph{Disco}) data sets is evaluated by validating appropriate RDF constraints assigned to several RDF constraint types.
First, we show the results of the evaluation of diverse data sets, then we give an overview over the evaluated data sets, and finally we provide details about the evaluation.

\subsection{Evaluation Results}

Table \ref{tab:disco-evaluation-results} shows the results of the evaluation of \emph{Disco} data sets.

\begin{table}[H]
  \scriptsize
	\centering
		\begin{tabular}{l|l}
      \textbf{Evaluation Criteria} & \textbf{Counts} \\		
      \hline
		\emph{Validated Triples} & 9,673,055 \\
		\emph{Validated Data Sets} & 1,526 \\
		\hline
		\emph{Constraint Violations} & 3,545,703 \\
		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & 2,437,922 (68.8\%) \\
		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & 473,574 (13.4\%) \\
    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & 634,207 (17.9\%) \\
		\hline
		\emph{Constraint (Most Constraint Violations)} & \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} (547,916) \\
		                                               & \emph{DISCO-C-COMPARISON-VARIABLES-02} (547,916) \\
		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{0}$))} & \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} (547,916) \\
		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{1}$))} & \emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-46} (468,807) \\
		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{2}$))} & \emph{DISCO-C-COMPARISON-VARIABLES-02} (547,916) \\
		\hline
		\emph{Constraint Types} & 52 (15\textbar 37)\tablefootnote{legend: absolute number (absolute number implemented \textbar  absolute number not yet implemented)} \\
		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 30 (57.7\%) \\
		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 22 (42.3\%) \\
		\hline
		\emph{Constraint Types (Most Constraints)} & 1. Existential Quantifications: 46 (32.4\%\textbar46\textbar0)\tablefootnote{legend: absolute number (percentage value \textbar  absolute number implemented \textbar  absolute number not yet implemented)} \\
		                                           & 2. Data Model Consistency: 7 (1\textbar6) \\
																							 & 3. Aggregation: 7 (0\textbar7) \\
		\emph{Constraint Type (Most Constraints ($\mathcal{SL}_{2}$))} & Existential Quantifications: 9 (9\textbar0) \\
		\hline
		\emph{Constraints} & 142 (77\textbar 65) \\
		\emph{Constraints} ($\mathcal{C}_{C}$) & 72 (50.7\%) \\
		\emph{Constraints} ($\mathcal{C}_{T}$) & 70 (49.3\%) \\
		\emph{Constraints ($\mathcal{SL}_{0}$)} & 75 (52.8\%\textbar44\textbar31)\\
		\emph{Constraints ($\mathcal{SL}_{1}$)} & 9 (6.3\%\textbar8\textbar1)\\
		\emph{Constraints ($\mathcal{SL}_{2}$)} & 58 (40.8\%\textbar25\textbar33)\\
		\end{tabular}
    \caption{Evaluation of Disco Data Sets - Evaluation Results}
		\label{tab:disco-evaluation-results}
\end{table}

%\begin{table}[H]
    %\begin{center}
    %\begin{tabular}{@{}lc@{}}
           %& \multicolumn{1}{c}{\textbf{Constraint Types}}
    %\\  \cmidrule{2-2}
    %\\       \textbf{Criteria (Counts)}
           %& \textbf{\rot{Existential Quantifications}}
    %\\ \midrule
		%\emph{Constraints / Constraint Type} & 46 \\
    %\bottomrule
    %\end{tabular}
    %\caption{Evaluation of Disco Data Sets - Evaluation Results (2)}
		%\label{tab:disco-evaluation-results-2}
    %\end{center}
%\end{table}

\subsection{Data Sets Overview}

Tables \ref{tab:disco-data-sets-abbreviations} and \ref{tab:disco-sparql-endpoints} give an overview over the evaluated \emph{Disco} data sets, their abbreviations, and publicly available SPARQL endpoints.
Table \ref{tab:disco-overview} comprehends the number of triples, data sets, and instances of multiple vocabulary-specific classes.

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Abbr.} & \textbf{Disco Data Sets} \\		
      \hline
    \emph{Missy} & \emph{Microdata Information System}\tablefootnote{\url{http://www.gesis.org/missy/eu/missy-home}} \\
		\emph{DwB} & \emph{DwB Discovery Portal}\tablefootnote{\url{http://dwb-dev.nsd.uib.no/portal}} \\
		\emph{DDA-SND} & \emph{DDI-RDF}\tablefootnote{\url{http://ddi-rdf.borsna.se/}} \\
		               & provided by the \emph{Danish Data Archive (DDA)}\tablefootnote{\url{http://samfund.dda.dk/dda/default-en.asp}} and Swedish National Data Service (SND)\tablefootnote{\url{http://snd.gu.se/en}} \\ 
		\end{tabular}
	\caption{Disco Data Sets Abbreviations}
	\label{tab:disco-data-sets-abbreviations}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccccccccccc@{}}
           & \multicolumn{9}{c}{\textbf{Counts}}
    \\  \cmidrule{2-10}
    \\       \textbf{Data Sets}
           & \textbf{\rot{triples}}
           & \textbf{\rot{disco:StudyGroup}}
           & \textbf{\rot{disco:Study}}
           & \textbf{\rot{disco:LogicalDataSet}}
           & \textbf{\rot{disco:Universe}}
					 & \textbf{\rot{disco:Variable}}
					 & \textbf{\rot{disco:Question}}
				   & \textbf{\rot{disco:SummaryStatistics}}
					 & \textbf{\rot{disco:CategoryStatistics}}
					 & \textbf{\rot{skos:Concept}}
    \\ \midrule
    \emph{Missy} & 5,068,838 & 6 & 45 & 159 & 1,125 & 21,040 & 0 & 0 & 0 & 147,193 \\
		\emph{DwB} & 2,332,802 & 0 & 1,387 & 1,367 & 2,796 & 446,806 & 0 & 0 & 0 & 0 \\
		\emph{DDA-SND} & 2,271,415 & 0 & 1,490 & 0 & 10,188 & 80,070 & 139,237 & 0 & 0 & 290,963 \\ 
		\hline
		\textbf{\emph{Total}} & 9,673,055 & & & 1,526 \\
    \bottomrule
    \end{tabular}
    \caption{Disco Data Sets Overview}
		\label{tab:disco-overview}
    \end{center}
\end{table}

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Data Sets} & \textbf{SPARQL Endpoint} \\		
      \hline
      \emph{Missy} & \url{http://svko-missy:8181/openrdf-workbench/repositories/native-java-store/summary} \\
			\emph{DwB} & \url{http://dwb-dev.nsd.uib.no/sparql} \\
			\emph{DDA-SND} & \url{http://ddi-rdf.borsna.se/endpoint/} \\
		\end{tabular}
	\caption{Disco SPARQL Endpoints}
	\label{tab:disco-sparql-endpoints}
\end{table}

\subsection{Detailed Evaluation}

In this sub section, we give details about the evaluation in form of diverse tables containing the number of constraint violations per evaluated data set and constraint of particular constraint types.

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Existential Quantifications (1)}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-02}\textsuperscript{***} & 7 & 17 & 1,490 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-03}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-04}\textsuperscript{*} & 11,021 & 445,381 & 62,260 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-05}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & 139,237 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-06}\textsuperscript{*} & 12 & 1,367 & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-07}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-08}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-09}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-10}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Existential Quantifications (1)}
		\label{tab:evaluation-disco-existential-quantifications-1}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Existential Quantifications (2)}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-11}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-12}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-13}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-14}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-15}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-16}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-17}\textsuperscript{*} & 159 & 1,367 & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-18}\textsuperscript{*} & 159 & 1,367 & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-19}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-20}\textsuperscript{*} & $\checkmark$ & 1,367 & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Existential Quantifications (2)}
		\label{tab:evaluation-disco-existential-quantifications-2}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Existential Quantifications (3)}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-21}\textsuperscript{*} & $\checkmark$ & 1,367 & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-22}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-23}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-24}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-25}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-26}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-27}\textsuperscript{***} & $\checkmark$ & 130 & 1,490 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-28}\textsuperscript{**} & 159 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-29}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-30}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Existential Quantifications (3)}
		\label{tab:evaluation-disco-existential-quantifications-3}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Existential Quantifications (4)}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-31}\textsuperscript{**} & 159 & 1,367 & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-32}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-33}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-34}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-35}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-36}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-37}\textsuperscript{*} & 18,625 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-38}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & 750 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-39}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-40}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & 139,237 \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Existential Quantifications (4)}
		\label{tab:evaluation-disco-existential-quantifications-4}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Existential Quantifications (5)}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-41}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-42}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-43}\textsuperscript{*} & 15,733 & 446,806 & 80,070 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-44}\textsuperscript{*} & 159 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-45}\textsuperscript{*} & 6,784 & 446,806 & 19,221 \\
		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-46}\textsuperscript{**} & 11,550 & 446,806 & 10,451 \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Existential Quantifications (5)}
		\label{tab:evaluation-disco-existential-quantifications-5}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Conditional Properties}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{ DISCO-C-CONDITIONAL-PROPERTIES-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & 80,070 \\
		\emph{ DISCO-C-CONDITIONAL-PROPERTIES-02}\textsuperscript{**} & 12 & $\checkmark$ & $\checkmark$ \\
		\emph{ DISCO-C-CONDITIONAL-PROPERTIES-03}\textsuperscript{**} & 90 & $\checkmark$ & 2,980 \\
		\emph{ DISCO-C-CONDITIONAL-PROPERTIES-04}\textsuperscript{***} & 6 & $\checkmark$ & $\checkmark$ \\
		\emph{ DISCO-C-CONDITIONAL-PROPERTIES-05}\textsuperscript{***} & 45 & 1,387 & 1,490 \\
		\emph{ DISCO-C-CONDITIONAL-PROPERTIES-06}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Conditional Properties}
		\label{tab:evaluation-disco-conditional-properties}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Provenance}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-PROVENANCE-01}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-PROVENANCE-02}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
		\emph{DISCO-C-PROVENANCE-03}\textsuperscript{*} & 159 & 1,367 & $\checkmark$ \\
		\emph{DISCO-C-PROVENANCE-04}\textsuperscript{*} & $\checkmark$ & 1,367 & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Provenance}
		\label{tab:evaluation-disco-provenance}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Labeling and Documentation}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-LABELING-AND-DOCUMENTATION-01}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-LABELING-AND-DOCUMENTATION-02}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
		\emph{DISCO-C-LABELING-AND-DOCUMENTATION-03}\textsuperscript{*} & 159 & 1,367 & $\checkmark$ \\
		\emph{DISCO-C-LABELING-AND-DOCUMENTATION-04}\textsuperscript{*} & $\checkmark$ & 1,367 & $\checkmark$ \\
		\emph{DISCO-C-LABELING-AND-DOCUMENTATION-05}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-LABELING-AND-DOCUMENTATION-06}\textsuperscript{*} & 21,040 & 446,806 & 80,070 \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Labeling and Documentation}
		\label{tab:evaluation-disco-labeling-and-documentation}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Data Model Consistency}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-DATA-MODEL-CONSISTENCY-01 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-DATA-MODEL-CONSISTENCY-02 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-DATA-MODEL-CONSISTENCY-03 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-DATA-MODEL-CONSISTENCY-04 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-DATA-MODEL-CONSISTENCY-05}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-DATA-MODEL-CONSISTENCY-06 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-DATA-MODEL-CONSISTENCY-07 (!)}\textsuperscript{***} \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Data Model Consistency}
		\label{tab:evaluation-disco-data-model-consistency}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Comparison}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-COMPARISON-VARIABLES-01 (!)}\textsuperscript{**} \\
		\emph{DISCO-C-COMPARISON-VARIABLES-02}\textsuperscript{***} & 21,040 & 446,806 & 80,070 \\
		\emph{DISCO-C-COMPARISON-VARIABLES-03 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-COMPARISON-VARIABLES-04}\textsuperscript{*} & 18,625 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-COMPARISON-VARIABLES-05}\textsuperscript{***} & 159 & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Comparison}
		\label{tab:evaluation-disco-comparison}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Mathematical Operations}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-MATHEMATICAL-OPERATIONS-01 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-MATHEMATICAL-OPERATIONS-02 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-MATHEMATICAL-OPERATIONS-03 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-MATHEMATICAL-OPERATIONS-04 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-MATHEMATICAL-OPERATIONS-05 (!)}\textsuperscript{***} \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Mathematical Operations}
		\label{tab:evaluation-disco-mathematical-operations}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Language Tags}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-LANGUAGE-TAG-MATCHING-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-LANGUAGE-TAG-CARDINALITY-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-LANGUAGE-TAG-CARDINALITY-02 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-LANGUAGE-TAG-CARDINALITY-03 (!)}\textsuperscript{*} \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Language Tags}
		\label{tab:evaluation-disco-language-tags}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Aggregation}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-AGGREGATION-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-AGGREGATION-02 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-AGGREGATION-03 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-AGGREGATION-04 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-AGGREGATION-05 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-AGGREGATION-06 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-AGGREGATION-07 (!)}\textsuperscript{*} \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Aggregation}
		\label{tab:evaluation-disco-aggregation}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Disco Constraints}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
    \emph{DISCO-C-ALLOWED-VALUES-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-LITERAL-RANGES-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-INVERSE-FUNCTIONAL-PROPERTIES-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-INVERSE-FUNCTIONAL-PROPERTIES-02}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-CLASS-SPECIFIC-PROPERTY-RANGE-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-MEMBERSHIP-IN-CONTROLLED-VOCABULARIES-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & \ding{55} \\
		\emph{DISCO-C-LITERAL-VALUE-COMPARISON-01}\textsuperscript{***} & $\checkmark$ & 1,299 & $\checkmark$ \\
		\emph{DISCO-C-CONTEXT-SPECIFIC-VALID-PROPERTIES-01}\textsuperscript{*} & 21,038 & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-DATA-PROPERTY-FACETS-01}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-DATA-PROPERTY-FACETS-02}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Disco Constraints (1)}
		\label{tab:evaluation-disco-disco-constraints-1}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Disco Constraints}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
		\emph{DISCO-C-VALUE-IS-VALID-FOR-DATATYPE-01}\textsuperscript{***} & 30 & 6,932 & $\checkmark$ \\
		\emph{DISCO-C-VALUE-IS-VALID-FOR-DATATYPE-02}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DISCO-C-SUBSUMPTION-01 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-CLASS-EQUIVALENCE-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-SUB-PROPERTIES-01 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-PROPERTY-DOMAIN-01 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-PROPERTY-RANGES-01 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-INVERSE-OBJECT-PROPERTIES-01 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-INVERSE-OBJECT-PROPERTIES-02 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-INVERSE-OBJECT-PROPERTIES-03 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-DISJOINT-PROPERTIES-01 (!)}\textsuperscript{***} \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Disco Constraints (2)}
		\label{tab:evaluation-disco-disco-constraints-2}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Disco Constraints}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
		\emph{DISCO-C-ASYMMETRIC-OBJECT-PROPERTIES-01 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-IRREFLEXIVE-OBJECT-PROPERTIES-01 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-CLASS-SPECIFIC-IRREFLEXIVE-OBJECT-PROPERTIES-01 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-CLASS-SPECIFIC-IRREFLEXIVE-OBJECT-PROPERTIES-02 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-DISJOINT-CLASSES-01 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-EQUIVALENT-PROPERTIES-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-LITERAL-PATTERN-MATCHING-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-DISJUNCTION-01 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-UNIVERSAL-QUANTIFICATIONS-01 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01 (!)}\textsuperscript{***} \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Disco Constraints (3)}
		\label{tab:evaluation-disco-disco-constraints-3}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Disco Constraints}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
		\emph{DISCO-C-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-01 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-CONTEXT-SPECIFIC-EXCLUSIVE-OR-OF-PROPERTY-GROUPS-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-IRI-PATTERN-MATCHING-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-ORDERING-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-ORDERING-02 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-ORDERING-03 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-STRING-OPERATIONS-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-CONTEXT-SPECIFIC-VALID-CLASSES-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-CONTEXT-SPECIFIC-VALID-PROPERTIES-01 (!)}\textsuperscript{*} \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Disco Constraints (4)}
		\label{tab:evaluation-disco-disco-constraints-4}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Disco Constraints}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
		\emph{DISCO-C-DEFAULT-VALUES-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-WHITESPACE-HANDLING-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-HTML-HANDLING-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-HTML-HANDLING-02 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-RECOMMENDED-PROPERTIES-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-HANDLE-RDF-COLLECTIONS-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-HANDLE-RDF-COLLECTIONS-02 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-USE-SUB-SUPER-RELATIONS-IN-VALIDATION-01 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-USE-SUB-SUPER-RELATIONS-IN-VALIDATION-02 (!)}\textsuperscript{*} \\
		\emph{DISCO-C-STRUCTURE-01 (!)}\textsuperscript{***} \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Disco Constraints (5)}
		\label{tab:evaluation-disco-disco-constraints-5}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccc@{}}
           & \multicolumn{3}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-4}
    \\       \textbf{Disco Constraints}
           & \rot{\emph{Missy}}
           & \rot{\emph{DwB}}
           & \rot{\emph{DDA-SND}}
    \\ \midrule
		\emph{DISCO-C-VOCABULARY-01 (!)}\textsuperscript{***} \\
		\emph{DISCO-C-HTTP-URI-SCHEME-VIOLATION (!)}\textsuperscript{***} \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Disco Data Sets - Disco Constraints (6)}
		\label{tab:evaluation-disco-disco-constraints-6}
    \end{center}
\end{table}

\section{Evaluation of Aggregated Metadata (\emph{Data Cube})}

In this section, the quality of the metadata on aggregated data (\emph{Data Cube}) data sets is evaluated by validating appropriate RDF constraints assigned to several RDF constraint types.
First, we show the results of the evaluation of diverse data sets, then we give an overview over the evaluated data sets, and finally we provide details about the evaluation.

\subsection{Evaluation Results}

Table \ref{tab:data-cube-evaluation-results} shows the results of the evaluation of \emph{Data Cube} data sets.

\begin{table}[H]
  \scriptsize
	\centering
		\begin{tabular}{l|l}
      \textbf{Evaluation Criteria} & \textbf{Counts} \\		
      \hline
		\emph{Validated Triples} & 3,775,983,610 \\
		\emph{Validated Data Sets} & 9,990 \\
		\hline
		\emph{Constraint Violations} & 45,635,846 \\
		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & 0 (0\%) \\
		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & 45,520,613 (99.75\%) \\
    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & 115,233 (0.25\%) \\
		\hline
		\emph{Constraint (Most Constraint Violations)} & \emph{DATA-MODEL-CONSISTENCY-05} (45,514,102) \\
		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{0}$))} & - \\
		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{1}$))} & \emph{DATA-MODEL-CONSISTENCY-05} (45,514,102) \\
		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{2}$))} & \emph{MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-02} \\
		                                                                    & (1,556) \\
		\hline
		\emph{Constraint Types} & 20 (7\textbar 13) \\
		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 5 (25\%) \\
		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 15 (75\%) \\
		\hline
		\emph{Constraint Types (Most Constraints)} & 1. Data Model Consistency: 11 (31.4\%\textbar10\textbar1) \\
		                                           & 2. Existential Quantifications: 4 (11.4\%\textbar4\textbar0) \\
		\emph{Constraint Type (Most Constraints ($\mathcal{SL}_{2}$))} & Data Model Consistency: 8 (22.9\%\textbar7\textbar1) \\
		\hline
		\emph{Constraints} & 35 (20\textbar 15) \\
		\emph{Constraints} ($\mathcal{C}_{C}$) & 16 (45.7\%\textbar12\textbar4) \\
		\emph{Constraints} ($\mathcal{C}_{T}$) & 19 (54.3\%\textbar8\textbar11) \\
		\emph{Constraints ($\mathcal{SL}_{0}$)} & 4 (11.4\%\textbar0\textbar4) \\
		\emph{Constraints ($\mathcal{SL}_{1}$)} & 3 (8.6\%\textbar3\textbar0) \\
		\emph{Constraints ($\mathcal{SL}_{2}$)} & 28 (80\%\textbar17\textbar11) \\
		\end{tabular}
    \caption{Evaluation of Data Cube Data Sets - Evaluation Results}
		\label{tab:data-cube-evaluation-results}
\end{table}

\subsection{Data Sets Overview}

There are websites giving an overview over available \emph{Data Cube} data sets\footnote{\url{http://270a.info/}; \url{http://datahub.io/de/dataset?tags=format-qb}; \url{http://ontologycentral.com/}}. 
Tables \ref{tab:data-cube-data-sets-abbreviations} and \ref{tab:data-cube-sparql-endpoints} give an overview over the evaluated \emph{Data Cube} data sets, their abbreviations, and publicly available SPARQL endpoints.
Table \ref{tab:data-cube-overview} comprehends the number of triples, data sets, and instances of multiple vocabulary-specific classes.

%\begin{table}
	%\centering
		%\begin{tabular}{l|c|c|c|c|c|c}
      %\textbf{Data Set} & \textbf{triples} & \textbf{data sets} & \textbf{data structure definitions} & \textbf{observations} & \textbf{slices} & \textbf{dimensions} \\		
      %\hline
      %European Central Bank (ECB)\tablefootnote{\url{http://www.ecb.europa.eu/home/html/index.en.html}} &  &  &  &  &  &  \\
			%UNESCO Institute for Statistics (UIS)\tablefootnote{\url{http://www.uis.unesco.org/Pages/default.aspx}} &  &  &  &  &  &  \\
			%International Monetary Fund (IMF)\tablefootnote{\url{http://www.imf.org/external/index.htm}} &  &  &  &  &  &  \\
			%Bundesamt für Statistik - Swiss Federal Statistics (BFS)\tablefootnote{\url{http://www.bfs.admin.ch/}} &  &  &  &  &  &  \\
			%Food and Agriculture Organization of the United Nations (FAO)\tablefootnote{\url{http://www.fao.org/home/en/}} &  &  &  &  &  &  \\
			%World Bank (WB)\tablefootnote{\url{http://www.worldbank.org/}} &  &  &  &  &  &  \\
			%Federal Reserve Board (FRB)\tablefootnote{\url{http://www.federalreserve.gov/}} &  &  &  &  &  &  \\
			%Transparency International (TI)\tablefootnote{\url{http://www.transparency.org/}} &  &  &  &  &  &  \\
			%Organisation for Economic Co-operation and Development (OECD)\tablefootnote{\url{http://www.oecd.org/}} &  &  &  &  &  &  \\
			%Bank for International Settlements (BIS)\tablefootnote{\url{http://www.bis.org/}} &  &  &  &  &  &  \\
			%Australian Bureau of Statistics (ABS)\tablefootnote{\url{http://abs.gov.au/}} &  &  &  &  &  &  \\
		%\end{tabular}
	%\caption{Data Cube Data Sets}
	%\label{tab:data-cube-data-sets}
%\end{table}

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Abbr.} & \textbf{Data Cube Data Sets} \\		
      \hline
    \emph{ECB} & \emph{European Central Bank}\tablefootnote{\url{http://www.ecb.europa.eu/home/html/index.en.html}} \\
		\emph{UIS} & \emph{UNESCO Institute for Statistics}\tablefootnote{\url{http://www.uis.unesco.org/Pages/default.aspx}} \\
		\emph{IMF} & \emph{International Monetary Fund}\tablefootnote{\url{http://www.imf.org/external/index.htm}} \\
		\emph{BFS} & \emph{Bundesamt für Statistik - Swiss Federal Statistics}\tablefootnote{\url{http://www.bfs.admin.ch/}} \\
		\emph{FAO} & \emph{Food and Agriculture Organization of the United Nations}\tablefootnote{\url{http://www.fao.org/home/en/}} \\
		\emph{WB} & \emph{World Bank}\tablefootnote{\url{http://www.worldbank.org/}} \\
		\emph{FRB} & \emph{Federal Reserve Board}\tablefootnote{\url{http://www.federalreserve.gov/}} \\
		\emph{TI} & \emph{Transparency International}\tablefootnote{\url{http://www.transparency.org/}} \\
		\emph{OECD} & \emph{Organisation for Economic Co-operation and Development}\tablefootnote{\url{http://www.oecd.org/}} \\
		\emph{BIS} & \emph{Bank for International Settlements}\tablefootnote{\url{http://www.bis.org/}} \\
		\emph{ABS} & \emph{Australian Bureau of Statistics}\tablefootnote{\url{http://abs.gov.au/}} \\
		\emph{IEEE-VIS} & \emph{IEEE VIS Source Data} \\
		\emph{ACORN-SAT} & \emph{Australian Climate Observations Reference Network - Surface Air Temperature Dataset} \\
		\emph{HDP} & \emph{HealthData.gov Platform (HDP) on the Semantic Web} \\
		\emph{Eurostat} & \emph{The Eurostat Linked Data} (SPARQL endpoint unavailable) \\
		\emph{Asturias} & \emph{Nomenclator Asturias} (SPARQL endpoint unavailable!) \\
		\emph{ISTAT} & \emph{ISTAT Immigration (LinkedOpenData.it)} (SPARQL endpoint unavailable) \\
		\emph{ICANE} & \emph{Statistical Office of Cantabria (Instituto Cántabro de Estadística, ICANE)} \\ 
		      & (SPARQL endpoint unavailable) \\
		\emph{EE-2009} & \emph{European Election Results 2009} (SPARQL endpoint unavailable) \\
		\emph{EU-B} & \emph{Standard Eurobarometer} (SPARQL endpoint unavailable) \\
		\emph{ECB-S} & \emph{European Central Bank Statistics (PublicData.eu)} (SPARQL endpoint unavailable) \\
		\emph{CPV-2008} & \emph{Common Procurement Vocabulary (CPV) 2008} (SPARQL endpoint unavailable) \\
		\emph{CPV-2003} & \emph{Common Procurement Vocabulary (CPV) 2003} (SPARQL endpoint unavailable) \\
		%GHI-2011 & Global Hunger Index (GHI) 2011 (dump) \\
		\end{tabular}
	\caption{Data Cube Data Sets Abbreviations}
	\label{tab:data-cube-data-sets-abbreviations}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccccccccccc@{}}
           & \multicolumn{5}{c}{\textbf{Counts}}
    \\  \cmidrule{2-6}
    \\       \textbf{Data Sets}
           & \textbf{\rot{triples}}
           & \textbf{\rot{qb:DataSet}}
           & \textbf{\rot{qb:DataStructureDefinition}}
           & \textbf{\rot{qb:Observation}}
           & \textbf{\rot{qb:Slice}}
    \\ \midrule
    \emph{ECB} & 468,899,474 & 55 & 46 & $>$11,000,000 & 428,698 \\
		\emph{UIS} & 10,400,534 & 5 & 5 & 1,437,651 & 0 &  \\
		\emph{IMF} & 35,688,446 & 4 & 8 & 3,603,719 & 0 &  \\
		\emph{BFS} & 1,533,743 & 0 & 0 & 8 & 0 &  \\
		\emph{FAO} & 53,000,000 & 10 & 10 & $>$7,100,000 & 0 \\
		\emph{WB} & 174,006,552 & 9,466 & 59 & $>$17,000,000 & 0 \\
		\emph{FRB} & 185,266,900 & 49 & 98 & $>$9,500,000 & 0 \\
		\emph{TI} & 52,233 & 6 & 6 & 3,928 & 0 \\
		\emph{OECD} & 304,995,160 & 136 & 140 & $>$12,000,000 & 0 \\
		\emph{BIS} & 54,197,482 & 6 & 12 & 3,606,466 & 47,914 \\
		\emph{ABS} & 2,357,400,000 & 253 & 257 & $>$11,000,000 & 0  \\
		\emph{IEEE-VIS} & 19,935,340 & 0 & 0 & 1,350 & 0 \\
		\emph{ACORN-SAT} & 98,381,319 & 0 & 4 & 0 & 0 \\
		\emph{HDP} & 12,226,427 & 0 & 0 & 0 & 0 \\
		%Eurostat & 8,000,000,000 &  &  &  &  &  \\
		%Asturias & 4,508,050 &  &  &  &  &  \\
		%ISTAT & 3,024,396 &  &  &  &  &  \\
		%ICANE & 52,412 &  &  &  &  &  \\
		%EE-2009 & 3,165 &  &  &  &  &  \\
		%EU-B & 1,193,494 &  &  &  &  &  \\
		%ECB-S & 10,000,000 &  &  &  &  &  \\
		%CPV-2008 & 803,311 &  &  &  &  &  \\
		%CPV-2003 & 546,135 &  &  &  &  &  \\
		%GHI-2011 & 19,369 (dump) &  &  &  &  &  \\
		\hline
		\textbf{Total} & 3,775,983,610 & 9,990 & & & & \\
    \bottomrule
    \end{tabular}
    \caption{Data Cube Data Sets Overview}
		\label{tab:data-cube-overview}
    \end{center}
\end{table}

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Data Sets} & \textbf{SPARQL Endpoints} \\		
      \hline
      \emph{ECB} & \url{http://ecb.270a.info/sparql} \\
			\emph{UIS} & \url{http://uis.270a.info/sparql} \\
			\emph{IMF} & \url{http://imf.270a.info/sparql} \\
			\emph{BFS} & \url{http://bfs.270a.info/sparql} \\
			\emph{FAO} & \url{http://fao.270a.info/sparql} \\
			\emph{WB} & \url{http://worldbank.270a.info/sparql} \\
			\emph{FRB} & \url{http://frb.270a.info/sparql} \\
			\emph{TI} & \url{http://transparency.270a.info/sparql} \\
			\emph{OECD} & \url{http://oecd.270a.info/sparql} \\
			\emph{BIS} & \url{http://bis.270a.info/sparql} \\
			\emph{ABS} & \url{http://abs.270a.info/sparql} \\
			\emph{ACORN-SAT} & \url{http://lab.environment.data.gov.au/sparql} \\
			\emph{HDP} & \url{http://healthdata.tw.rpi.edu/sparql} \\
		\end{tabular}
	\caption{Data Cube SPARQL Endpoints}
	\label{tab:data-cube-sparql-endpoints}
\end{table}

\subsection{Detailed Evaluation}

In this sub section, we give details about the evaluation in form of diverse tables containing the number of constraint violations per evaluated data set and constraint of particular constraint types.

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccccccc@{}}
           & \multicolumn{7}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-8}
    \\       \textbf{Data Model Consistency}
           & \rot{\emph{ECB}}
           & \rot{\emph{UIS}}
           & \rot{\emph{IMF}}
           & \rot{\emph{BFS}}
           & \rot{\emph{FAO}}
					 & \rot{\emph{WB}}
					 & \rot{\emph{FRB}}
    \\ \midrule
    \emph{DATA-MODEL-CONSISTENCY-01}\textsuperscript{**} & $\checkmark$ (2) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \emph{DATA-MODEL-CONSISTENCY-02}\textsuperscript{***} & $\checkmark$ (2) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \emph{DATA-MODEL-CONSISTENCY-03}\textsuperscript{***} & $\checkmark$ (2) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \emph{DATA-MODEL-CONSISTENCY-04}\textsuperscript{***} & $\checkmark$ (6) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 14,372 \\
		\emph{DATA-MODEL-CONSISTENCY-05}\textsuperscript{**} & 1,198,352 (50) & \ding{55} & \ding{55} & $\checkmark$ & \ding{55} & $\checkmark$ & 16,175,814 (42) \\
		\emph{DATA-MODEL-CONSISTENCY-06}\textsuperscript{***} & $\checkmark$ (2) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DATA-MODEL-CONSISTENCY-07}\textsuperscript{***} & $\checkmark$ (9) & $\checkmark$ & 99,091 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ (1) \\
		\emph{DATA-MODEL-CONSISTENCY-08}\textsuperscript{***} & $\checkmark$ (2) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DATA-MODEL-CONSISTENCY-09}\textsuperscript{***} & $\checkmark$ (2) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DATA-MODEL-CONSISTENCY-10}\textsuperscript{***} (!) & - & - & - & - & - & - & - \\
		\emph{DATA-MODEL-CONSISTENCY-11}\textsuperscript{**} & 6,511 (10) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Data Cube Data Sets - Data Model Consistency (1)}
		\label{evaluation-of-data-cube-data-sets-data-model-consistency-1}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccccccc@{}}
           & \multicolumn{7}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-8}
    \\       \textbf{Data Model Consistency}
					 & \rot{\emph{TI}}
					 & \rot{\emph{OECD}}
					 & \rot{\emph{BIS}}
					 & \rot{\emph{ABS}}
					 & \rot{\emph{IEEE-VIS}}
					 & \rot{\emph{ACORN-SAT}}
					 & \rot{\emph{HDP}}
    \\ \midrule
    \emph{DATA-MODEL-CONSISTENCY-01}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \emph{DATA-MODEL-CONSISTENCY-02}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 8 & $\checkmark$ \\
    \emph{DATA-MODEL-CONSISTENCY-03}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \emph{DATA-MODEL-CONSISTENCY-04}\textsuperscript{***} & $\checkmark$ & $\checkmark$& $\checkmark$ & $\checkmark$ (6) & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DATA-MODEL-CONSISTENCY-05}\textsuperscript{**} & $\checkmark$ & 21,142,838 (116) & \ding{55} &  6,997,098 (246) & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DATA-MODEL-CONSISTENCY-06}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DATA-MODEL-CONSISTENCY-07}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ (8) & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DATA-MODEL-CONSISTENCY-08}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DATA-MODEL-CONSISTENCY-09}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{DATA-MODEL-CONSISTENCY-10}\textsuperscript{***} (!) & - & - & - & - & - & - & - \\
		\emph{DATA-MODEL-CONSISTENCY-11}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Data Cube Data Sets - Data Model Consistency (2)}
		\label{evaluation-of-data-cube-data-sets-data-model-consistency-1}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccccccccccccc@{}}
           & \multicolumn{14}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-15}
    \\       \textbf{Existential Quantifications}
           & \rot{\emph{ECB}}
           & \rot{\emph{UIS}}
           & \rot{\emph{IMF}}
           & \rot{\emph{BFS}}
           & \rot{\emph{FAO}}
					 & \rot{\emph{WB}}
					 & \rot{\emph{FRB}}
					 & \rot{\emph{TI}}
					 & \rot{\emph{OECD}}
					 & \rot{\emph{BIS}}
					 & \rot{\emph{ABS}}
					 & \rot{\emph{IEEE-VIS}}
					 & \rot{\emph{ACORN-SAT}}
					 & \rot{\emph{HDP}}
    \\ \midrule
		\emph{EXISTENTIAL-QUANTIFICATIONS-01}\textsuperscript{***} & 9 & $\checkmark$ & 11 & 7 & 8 & 77 & 8 & 9 & 7 & 8 & 7 & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{EXISTENTIAL-QUANTIFICATIONS-02}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{EXISTENTIAL-QUANTIFICATIONS-03}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 59 & $\checkmark$ & 6 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 4 & $\checkmark$ \\
		\emph{EXISTENTIAL-QUANTIFICATIONS-04}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Data Cube Data Sets - Existential Quantifications}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccccccccc@{}}
           & \multicolumn{10}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-11}
    \\       \textbf{Cardinality Restrictions}
           & \rot{\emph{ECB}}
           & \rot{\emph{UIS}}
           & \rot{\emph{IMF}}
           & \rot{\emph{BFS}}
           & \rot{\emph{FAO}}
					 & \rot{\emph{WB}}
					 & \rot{\emph{FRB}}
					 & \rot{\emph{TI}}
					 & \rot{\emph{OECD}}
					 & \rot{\emph{BIS}}
    \\ \midrule
		\emph{MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01 (!)}\textsuperscript{***} & - & - & - & - & - & - & - & - & - & - \\
		\emph{MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-02}\textsuperscript{***} & \ding{55} & 118 & 8 & 8 & 30 & $\checkmark$ & 30 & $\checkmark$ & \ding{55} & 12 \\
		\emph{MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 1 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Data Cube Data Sets - Cardinality Restrictions (1)}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccc@{}}
           & \multicolumn{4}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-5}
    \\       \textbf{Cardinality Restrictions}
					 & \rot{\emph{ABS}}
					 & \rot{\emph{IEEE-VIS}}
					 & \rot{\emph{ACORN-SAT}}
					 & \rot{\emph{HDP}}
    \\ \midrule
		\emph{MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01 (!)}\textsuperscript{***} & - & - & - & - \\
		\emph{MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-02}\textsuperscript{***} & \ding{55} & 1,350 & $\checkmark$ & $\checkmark$ \\
		\emph{MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01}\textsuperscript{***} & $\checkmark$ (2) & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Data Cube Data Sets - Cardinality Restrictions (2)}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccccccccccccc@{}}
           & \multicolumn{14}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-15}
    \\       \textbf{Structure}
           & \rot{\emph{ECB}}
           & \rot{\emph{UIS}}
           & \rot{\emph{IMF}}
           & \rot{\emph{BFS}}
           & \rot{\emph{FAO}}
					 & \rot{\emph{WB}}
					 & \rot{\emph{FRB}}
					 & \rot{\emph{TI}}
					 & \rot{\emph{OECD}}
					 & \rot{\emph{BIS}}
					 & \rot{\emph{ABS}}
					 & \rot{\emph{IEEE-VIS}}
					 & \rot{\emph{ACORN-SAT}}
					 & \rot{\emph{HDP}}
    \\ \midrule
		\emph{STRUCTURE-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{STRUCTURE-02}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Data Cube Data Sets - Structure}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccccccccccccc@{}}
           & \multicolumn{14}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-15}
    \\       \textbf{Constraints}
           & \rot{\emph{ECB}}
           & \rot{\emph{UIS}}
           & \rot{\emph{IMF}}
           & \rot{\emph{BFS}}
           & \rot{\emph{FAO}}
					 & \rot{\emph{WB}}
					 & \rot{\emph{FRB}}
					 & \rot{\emph{TI}}
					 & \rot{\emph{OECD}}
					 & \rot{\emph{BIS}}
					 & \rot{\emph{ABS}}
					 & \rot{\emph{IEEE-VIS}}
					 & \rot{\emph{ACORN-SAT}}
					 & \rot{\emph{HDP}}
    \\ \midrule
		\emph{PROPERTY-DOMAIN-01 (!)}\textsuperscript{***} &  &  &  &  &  &  &  &  &  &  &  &  \\
		\emph{PROPERTY-RANGES-01 (!)}\textsuperscript{***} &  &  &  &  &  &  &  &  &  &  &  &  \\
		\emph{DISJOINT-PROPERTIES-01 (!)}\textsuperscript{***} &  &  &  &  &  &  &  &  &  &  &  &  \\
		\emph{DISJOINT-CLASSES-01 (!)}\textsuperscript{***} &  &  &  &  &  &  &  &  &  &  &  &  \\
		\emph{EQUIVALENT-PROPERTIES-01 (!)}\textsuperscript{*} &  &  &  &  &  &  &  &  &  &  &  &  \\
		\emph{UNIVERSAL-QUANTIFICATIONS-01 (!)}\textsuperscript{***} &  &  &  &  &  &  &  &  &  &  &  &  \\
		\emph{MEMBERSHIP-IN-CONTROLLED-VOCABULARIES-01 (!)}\textsuperscript{***} &  &  &  &  &  &  &  &  &  &  &  &  \\
		\emph{CONTEXT-SPECIFIC-VALID-CLASSES-01 (!)}\textsuperscript{*} &  &  &  &  &  &  &  &  &  &  &  &  \\
		\emph{CONTEXT-SPECIFIC-VALID-PROPERTIES-01 (!)}\textsuperscript{*} &  &  &  &  &  &  &  &  &  &  &  &  \\
		\emph{RECOMMENDED-PROPERTIES-01 (!)}\textsuperscript{*} &  &  &  &  &  &  &  &  &  &  &  &  \\
		\emph{VALUE-IS-VALID-FOR-DATATYPE-01 (!)}\textsuperscript{***} &  &  &  &  &  &  &  &  &  &  &  &  \\
		\emph{VOCABULARY-01 (!)}\textsuperscript{***} &  &  &  &  &  &  &  &  &  &  &  &  \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Data Cube Data Sets - Constraints (1)}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccccccccccccc@{}}
           & \multicolumn{14}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-15}
    \\       \textbf{Constraints}
           & \rot{\emph{ECB}}
           & \rot{\emph{UIS}}
           & \rot{\emph{IMF}}
           & \rot{\emph{BFS}}
           & \rot{\emph{FAO}}
					 & \rot{\emph{WB}}
					 & \rot{\emph{FRB}}
					 & \rot{\emph{TI}}
					 & \rot{\emph{OECD}}
					 & \rot{\emph{BIS}}
					 & \rot{\emph{ABS}}
					 & \rot{\emph{IEEE-VIS}}
					 & \rot{\emph{ACORN-SAT}}
					 & \rot{\emph{HDP}}
    \\ \midrule
		\emph{HTTP-URI-SCHEME-VIOLATION (!)}\textsuperscript{***} \\
    \bottomrule
    \end{tabular}
    \caption{Evaluation of Data Cube Data Sets - Constraints (2)}
    \end{center}
\end{table}

\section{Evaluation of Thesauri (\emph{SKOS})}

In this section, the quality of the metadata on thesauri (\emph{SKOS}) is evaluated by validating appropriate RDF constraints assigned to several RDF constraint types.
First, we show the results of the evaluation of diverse thesauri, then we give an overview over the evaluated thesauri, and finally we provide details about the evaluation.

\subsection{Evaluation Results}

Table \ref{tab:thesauri-evaluation-results} shows the results of the evaluation of \emph{thesauri}.

\begin{table}[H]
  \scriptsize
	\centering
		\begin{tabular}{l|l}
      \textbf{Evaluation Criteria} & \textbf{Counts} \\		
      \hline
		\emph{Validated Triples} & 477,737,281 \\
		\emph{Validated Data Sets} & 4,178 \\
		\hline
		\emph{Constraint Violations} & 5,540,988 \\
		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & 2,281,740 (41.2\%) \\
		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & 3,259,248 (58.8\%) \\
    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & 0 (0\%) \\
		\hline
		\emph{Constraint (Most Constraint Violations)} & \emph{LANGUAGE-TAG-CARDINALITY-01} (2,508,903) \\
		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{0}$))} & \emph{LABELING-AND-DOCUMENTATION-06} (1,022,362) \\
		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{1}$))} & \emph{LANGUAGE-TAG-CARDINALITY-01} (2,508,903) \\
		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{2}$))} & - \\
		\hline
		\emph{Constraint Types} & 14 (4\textbar 10) \\
		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 5 (35.7\%) \\
		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 9 (64.3\%) \\
		\hline
		\emph{Constraint Types (Most Constraints)} & 1. Structure: 10 (28.6\%\textbar8\textbar2) \\
		                                           & 2. Labeling and Documentation: 6 (17.1\%\textbar5\textbar1) \\
																							 & 3. Language Tag Cardinality: 4 (11.4\%\textbar4\textbar0) \\
		\emph{Constraint Type (Most Constraints ($\mathcal{SL}_{2}$))} & Structure: 1 (0\textbar1) \\
		\hline
		\emph{Constraints} & 35 (17\textbar 18) \\
		\emph{Constraints} ($\mathcal{C}_{C}$) & 21 (60\%\textbar13\textbar8) \\
		\emph{Constraints} ($\mathcal{C}_{T}$) & 14 (40\%\textbar4\textbar10) \\
		\emph{Constraints ($\mathcal{SL}_{0}$)} & 21 (60\%\textbar12\textbar9) \\
		\emph{Constraints ($\mathcal{SL}_{1}$)} & 5 (14.3\%\textbar5\textbar0) \\
		\emph{Constraints ($\mathcal{SL}_{2}$)} & 9 (25.7\%\textbar0\textbar9) \\
		\end{tabular}
    \caption{Evaluation of Thesauri Data Sets - Evaluation Results}
		\label{tab:thesauri-evaluation-results}
\end{table}

\subsection{Data Sets Overview}

There is a website giving an overview over available \emph{SKOS} data sets\footnote{\url{http://datahub.io/de/dataset?tags=format-skos}}
and another one giving an overview over available thesauri\footnote{\url{http://datahub.io/de/dataset?tags=thesaurus}}.
Tables \ref{tab:thesauri-abbreviations} and \ref{tab:thesauri-sparql-endpoints} give an overview over the evaluated thesauri, their abbreviations, and publicly available SPARQL endpoints.
Table \ref{tab:thesauri-overview} comprehends the number of triples, data sets, and instances of multiple vocabulary-specific classes.

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Abbr.} & \textbf{Thesauri} \\		
      \hline
    \emph{TheSoz} & \emph{Thesaurus for the Social Sciences}\tablefootnote{\url{http://www.ecb.europa.eu/home/html/index.en.html}} \\
	  \emph{STW} & \emph{Thesaurus for Economics}\tablefootnote{\url{http://zbw.eu/stw/versions/latest/about}} \\
	  \emph{AGROVOC} & \emph{AGROVOC Multilingual agricultural thesaurus}\tablefootnote{\url{http://202.45.139.84:10035/catalogs/fao/repositories/agrovoc}} \\
		\emph{UNESCO} & \emph{UNESCO Thesaurus}\tablefootnote{\url{http://skos.um.es/sparql/}} \\
		\emph{TGN} & \emph{The Getty Thesaurus of Geographic Names}\tablefootnote{\url{http://vocab.getty.edu/sparql}} \\
		\emph{EARTh} & \emph{Environmental Applications Reference Thesaurus}\tablefootnote{\url{http://linkeddata.ge.imati.cnr.it/resource/EARTh/}} \\
		\emph{ODT} & \emph{Open Data Thesaurus}\tablefootnote{\url{http://vocabulary.semantic-web.at/PoolParty/wiki/OpenData}} \\
		\emph{SLD} & \emph{Spanish Linguistic Datasets}\tablefootnote{\url{http://linguistic.linkeddata.es}} \\
		\emph{SSWT} & \emph{Social Semantic Web Thesaurus}\tablefootnote{\url{http://vocabulary.semantic-web.at/PoolParty/wiki/semweb}} \\
		\emph{GBA-GU} & \emph{Thesaurus of the Geological Survey of Austria (GBA) - Geology Unit}\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
		\emph{GBA-GTS} & \emph{Thesaurus of the Geological Survey of Austria (GBA) - Geologic Time Scale}\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
		\emph{GBA-L} & \emph{Thesaurus of the Geological Survey of Austria (GBA) - Lithology}\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
		\emph{GBA-LU} & \emph{Thesaurus of the Geological Survey of Austria (GBA) - Lithotectonic Unit}\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
		\emph{GEMET} & \emph{GEneral Multilingual Environmental Thesaurus}\tablefootnote{\url{http://www.eionet.europa.eu/gemet/}} \\
		\emph{EuroVoc} & \emph{EuroVoc}\tablefootnote{\url{http://open-data.europa.eu/de/data/dataset/eurovoc}} \\
		\emph{CECCT} & \emph{Clean Energy and Climate Change Thesaurus}\tablefootnote{\url{http://data.reegle.info/thesaurus/guide}} \\
		\end{tabular}
	\caption{Thesauri Abbreviations}
	\label{tab:thesauri-abbreviations}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lccccccccccc@{}}
           & \multicolumn{7}{c}{\textbf{Counts}}
    \\  \cmidrule{2-8}
    \\       \textbf{Thesauri}
           & \textbf{\rot{triples}}
           & \textbf{\rot{skos:ConceptScheme}}
           & \textbf{\rot{sko:Concept}}
           & \textbf{\rot{skos:broader}}
           & \textbf{\rot{skos:narrower}}
					 & \textbf{\rot{skos:hasTopConcept}}
					 & \textbf{\rot{skos:inScheme}}
    \\ \midrule
    \emph{TheSoz} & 439,153 & 1 & 8,426 & 13,705 & 13,706 & 0 & 48,529 \\
	  \emph{STW} & 221,668 & 1 & 13,468 & 13,732 & 13732 & 7 & 13,180 \\
	  \emph{AGROVOC} & 6,080,477 & 1 & 32,310 & 33,507 & 33,507 & 25 & 32,310 \\
		\emph{UNESCO} & 288,346 & 9 & 26,714 & 20,028 & 20,028 & 607 & 32,009 \\
		\emph{TGN} & 16,112,321 & 8 & 2,898,775 & 0 & 0 & 0 & 1,453,767\\
		\emph{EARTh} & 9,287,364 & 11 & 295,375 & 288,208 & 93,827 & 479 & 295,376 \\
		\emph{ODT} & 3,290 & 6 & 108 & 93 & 93 & 30 & 0 \\
		\emph{SLD} & 7,629,211 & 0 & 31,195 & 0 & 0 & 0 & 0 \\
		\emph{SSWT} & 64,698 & 9 & 2,127 & 2,300 & 2,301 & 38 & 0 \\
		\emph{GBA-GU} & 25,718 & 3 & 878 & 1,005 & 1,005 & 14 & 0 \\
		\emph{GBA-GTS} & 7,875 & 3 & 213 & 208 & 208 & 5 & 0 \\
		\emph{GBA-L} & 9,317 & 1 & 249 & 249 & 249 & 4 & 0 \\
		\emph{GBA-LU} & 9,504 & 3 & 364 & 359 & 359 & 7 & 0 \\
		\emph{GEMET} & 372,889,229 & 3,680 & 414,659 & 62,193 & 21,685 & 30,806 & 409,290 \\
		\emph{EuroVoc} & 64,477,774 & 439 & 79,557 & 6,922 & 0 & 532 & 14,428 \\
		\emph{CECCT} & 191,336 & 3 & 3,419 & 3,761 & 3,762 & 28 & 0 \\
		\hline
		\textbf{Total} & 477,737,281 & 4,178 & & & & \\
    \bottomrule
    \end{tabular}
    \caption{Thesauri Overview}
		\label{tab:thesauri-overview}
    \end{center}
\end{table}

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Thesauri} & \textbf{SPARQL Endpoints} \\		
      \hline
      \emph{TheSoz} & \url{http://lod.gesis.org/thesoz/sparql} \\
			\emph{STW} & \url{http://zbw.eu/beta/sparql/stw/query} \\
			\emph{AGROVOC} & \url{http://202.45.139.84:10035/catalogs/fao/repositories/agrovoc} \\
			\emph{UNESCO} & \url{http://skos.um.es/sparql/} \\
			\emph{TGN} & \url{http://vocab.getty.edu/} \\
			\emph{EARTh} & \url{http://linkeddata.ge.imati.cnr.it:8890/sparql} \\
			\emph{ODT} & \url{http://vocabulary.semantic-web.at/PoolParty/sparql/OpenData} \\
			\emph{SLD} & \url{http://linguistic.linkeddata.es/sparql} \\
			\emph{SSWT} & \url{http://vocabulary.semantic-web.at/PoolParty/sparql/semweb} \\
			\emph{GBA-GU} & \url{http://resource.geolba.ac.at/PoolParty/sparql/GeologicUnit} \\
			\emph{GBA-GTS} & \url{http://resource.geolba.ac.at/PoolParty/sparql/GeologicTimeScale} \\
			\emph{GBA-L} & \url{http://resource.geolba.ac.at/PoolParty/sparql/lithology} \\
			\emph{GBA-LU} & \url{http://resource.geolba.ac.at/PoolParty/sparql/tectonicunit} \\
			\emph{GEMET} & \url{http://semantic.eea.europa.eu/sparql} \\
			\emph{EuroVoc} & \url{http://open-data.europa.eu/de/linked-data} \\
			\emph{CECCT} & \url{http://poolparty.reegle.info/PoolParty/sparql/glossary}
		\end{tabular}
	\caption{Thesauri SPARQL Endpoints}
	\label{tab:thesauri-sparql-endpoints}
\end{table}

\subsection{Detailed Evaluation}

In this sub section, we give details about the evaluation in form of diverse tables containing the number of constraint violations per evaluated data set and constraint of particular constraint types.

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccccccccccc@{}}
           & \multicolumn{12}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-13}
    \\       \textbf{Data Model Consistency}
           & \emph{\rot{TheSoz}}
           & \emph{\rot{STW}}
           & \emph{\rot{AGROVOC}}
					 & \emph{\rot{TGN}}
           & \emph{\rot{UNESCO}}
					 & \emph{\rot{ODT}}
					 & \emph{\rot{SSWT}}
					 & \emph{\rot{GBA-GU}}
					 & \emph{\rot{GBA-GTS}}
					 & \emph{\rot{GBA-L}}
					 & \emph{\rot{GBA-LU}}
					 & \emph{\rot{CECCT}}
    \\ \midrule
    \emph{DATA-MODEL-CONSISTENCY-01 (!)}\textsuperscript{*} &  &  &  &  &  & \\
    \emph{DATA-MODEL-CONSISTENCY-02 (!)}\textsuperscript{*} &  &  &  &  &  & \\
    \emph{DATA-MODEL-CONSISTENCY-03 (!)}\textsuperscript{*} &  &  &  &  &  & \\
    \bottomrule
    \end{tabular}
    \caption{Thesauri Evaluation - Data Model Consistency (1)}
		\label{tab:thesauri-evaluation-data-model-consistency-1}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccc@{}}
           & \multicolumn{4}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-5}
    \\       \textbf{Data Model Consistency}
					 & \emph{\rot{EARTh}}
					 & \emph{\rot{GEMET}}
					 & \emph{\rot{EuroVoc}}
					 & \emph{\rot{SLD}}
    \\ \midrule
    \emph{DATA-MODEL-CONSISTENCY-01 (!)}\textsuperscript{*} \\
    \emph{DATA-MODEL-CONSISTENCY-02 (!)}\textsuperscript{*} \\
    \emph{DATA-MODEL-CONSISTENCY-03 (!)}\textsuperscript{*} \\
    \bottomrule
    \end{tabular}
    \caption{Thesauri Evaluation - Data Model Consistency (2)}
		\label{tab:thesauri-evaluation-data-model-consistency-2}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccccccccccc@{}}
           & \multicolumn{12}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-13}
    \\       \textbf{Labeling and Documentation}
           & \emph{\rot{TheSoz}}
           & \emph{\rot{STW}}
           & \emph{\rot{AGROVOC}}
					 & \emph{\rot{TGN}}
           & \emph{\rot{UNESCO}}
					 & \emph{\rot{ODT}}
					 & \emph{\rot{SSWT}}
					 & \emph{\rot{GBA-GU}}
					 & \emph{\rot{GBA-GTS}}
					 & \emph{\rot{GBA-L}}
					 & \emph{\rot{GBA-LU}}
					 & \emph{\rot{CECCT}}
    \\ \midrule
		\emph{LABELING-AND-DOCUMENTATION-01}\textsuperscript{*} & 8,426 & 11,508 & 19,829 & 1,110 & \ding{55} & 36 & 1,475 & 5 & 2 & $\checkmark$ & 107 & 486 \\
		\emph{LABELING-AND-DOCUMENTATION-02}\textsuperscript{*} & $>$1 & \ding{55} & $>$100 & 287 & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{LABELING-AND-DOCUMENTATION-03}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & 1 & 14,114 & \ding{55} & $\checkmark$ & $\checkmark$ & 1 & $\checkmark$ & $\checkmark$ & 1 & $\checkmark$ \\
		\emph{LABELING-AND-DOCUMENTATION-04 (!)}\textsuperscript{*} &  &  &  &  &  & & &  \\
		\emph{LABELING-AND-DOCUMENTATION-05}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & 4 & $\checkmark$ & 1 & 2 & 2 & 1 & $\checkmark$ & $\checkmark$ & $\checkmark$ & 7 \\
		\emph{LABELING-AND-DOCUMENTATION-06}\textsuperscript{*} & 975,340 & $\checkmark$ & $\checkmark$ & 2 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
    \bottomrule
    \end{tabular}
    \caption{Thesauri Evaluation - Labeling and Documentation (1)}
		\label{tab:thesauri-evaluation-labeling-and-documentation-1}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccc@{}}
           & \multicolumn{4}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-5}
    \\       \textbf{Labeling and Documentation}
					 & \emph{\rot{EARTh}}
					 & \emph{\rot{GEMET}}
					 & \emph{\rot{EuroVoc}}
					 & \emph{\rot{SLD}}
    \\ \midrule
		\emph{LABELING-AND-DOCUMENTATION-01}\textsuperscript{*}& 264,687 & \ding{55} & 54,911 & 31,195 \\
		\emph{LABELING-AND-DOCUMENTATION-02}\textsuperscript{*} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
		\emph{LABELING-AND-DOCUMENTATION-03}\textsuperscript{*} & 2 & \ding{55} & 55,556 & 31,195 \\
		\emph{LABELING-AND-DOCUMENTATION-04 (!)}\textsuperscript{*} & \\
		\emph{LABELING-AND-DOCUMENTATION-05}\textsuperscript{*} & 39 & \ding{55} & \ding{55} & 978 \\
		\emph{LABELING-AND-DOCUMENTATION-06}\textsuperscript{*} &  302 & 46,718 & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Thesauri Evaluation - Labeling and Documentation (2)}
		\label{tab:thesauri-evaluation-labeling-and-documentation-2}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccccccccccc@{}}
           & \multicolumn{12}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-13}
    \\       \textbf{Structure}
           & \emph{\rot{TheSoz}}
           & \emph{\rot{STW}}
           & \emph{\rot{AGROVOC}}
					 & \emph{\rot{TGN}}
           & \emph{\rot{UNESCO}}
					 & \emph{\rot{ODT}}
					 & \emph{\rot{SSWT}}
					 & \emph{\rot{GBA-GU}}
					 & \emph{\rot{GBA-GTS}}
					 & \emph{\rot{GBA-L}}
					 & \emph{\rot{GBA-LU}}
					 & \emph{\rot{CECCT}}
    \\ \midrule
		\emph{STRUCTURE-01}\textsuperscript{**} & 1 & 1,074 & $\checkmark$ & $\checkmark$ & 1 & 5 & 1 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{STRUCTURE-02 (!)}\textsuperscript{*} &  &  &  &  &  & \\
		\emph{STRUCTURE-03}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 84 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{STRUCTURE-04}\textsuperscript{*} & 2,906 & 8,046 & 726 & $\checkmark$ & 3,840 & 12 & 124 & 84 & 256 & 68 & 22 & 2,422 \\
		\emph{STRUCTURE-05}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & \ding{55} & 90 & 5,150 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 9,864 \\
		\emph{STRUCTURE-06}\textsuperscript{*} & 1,457 & 37 & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & 4 & 1 & 1 & 64 & $\checkmark$ & 136 \\
		\emph{STRUCTURE-07}\textsuperscript{**} & 40 & 5,370 & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{STRUCTURE-08 (!)}\textsuperscript{***} &  &  &  &  &  & \\
		\emph{STRUCTURE-09}\textsuperscript{*} & 7,897 & 19,844 & 99 & $\checkmark$ & 552 & 2 & 16 & 26 & $\checkmark$ & $\checkmark$ & $\checkmark$ & 82 \\
		\emph{STRUCTURE-10}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Thesauri Evaluation - Structure (1)}
		\label{tab:thesauri-evaluation-structure-1}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccc@{}}
           & \multicolumn{4}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-5}
    \\       \textbf{Structure}
					 & \emph{\rot{EARTh}}
					 & \emph{\rot{GEMET}}
					 & \emph{\rot{EuroVoc}}
					 & \emph{\rot{SLD}}
    \\ \midrule
		\emph{STRUCTURE-01}\textsuperscript{**} & 18,240 & \ding{55} & 55,757 & 31,195 \\
		\emph{STRUCTURE-02 (!)}\textsuperscript{*} & \\
		\emph{STRUCTURE-03}\textsuperscript{**} & 39 & 4,244 & $\checkmark$ & $\checkmark$ \\
		\emph{STRUCTURE-04}\textsuperscript{*} & 11,286 & 74 & $\checkmark$ & $\checkmark$ \\
		\emph{STRUCTURE-05}\textsuperscript{*} & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ \\
		\emph{STRUCTURE-06}\textsuperscript{*} & 239,346 & \ding{55} & 13,876 & $\checkmark$ \\
		\emph{STRUCTURE-07}\textsuperscript{**} & 110,015 & \ding{55} & 366,155 & 155,975 \\
		\emph{STRUCTURE-08 (!)}\textsuperscript{***} & \\
		\emph{STRUCTURE-09}\textsuperscript{*} & 107,195 & 32 & $\checkmark$ & $\checkmark$ \\
		\emph{STRUCTURE-10}\textsuperscript{**} & 27 & 2,122 & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Thesauri Evaluation - Structure (2)}
		\label{tab:thesauri-evaluation-structure-2}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccccccccccc@{}}
           & \multicolumn{12}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-13}
    \\       \textbf{Language Tag Cardinality}
           & \emph{\rot{TheSoz}}
           & \emph{\rot{STW}}
           & \emph{\rot{AGROVOC}}
					 & \emph{\rot{TGN}}
           & \emph{\rot{UNESCO}}
					 & \emph{\rot{ODT}}
					 & \emph{\rot{SSWT}}
					 & \emph{\rot{GBA-GU}}
					 & \emph{\rot{GBA-GTS}}
					 & \emph{\rot{GBA-L}}
					 & \emph{\rot{GBA-LU}}
					 & \emph{\rot{CECCT}}
    \\ \midrule
		\emph{LANGUAGE-TAG-CARDINALITY-01}\textsuperscript{**} & 9,435 & 13,468 & 98,894 & $\checkmark$ &  & 541 & 10,147 & 5,117 & 2,061 & 1,742 & 2,272 & 15,550 \\
		\emph{LANGUAGE-TAG-CARDINALITY-02}\textsuperscript{*} & 8,222 & 36,936 & \ding{55} & $\checkmark$ &  & 265 & 3,627 & 2,212 & 635 & 631 & 1,253 & 9,607 \\
		\emph{LANGUAGE-TAG-CARDINALITY-03}\textsuperscript{*} & 8,222 & $\checkmark$ & 135 & $\checkmark$ &  & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
		\emph{LANGUAGE-TAG-CARDINALITY-04}\textsuperscript{*} & $\checkmark$ & 476 & \ding{55} & 50 &  & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Thesauri Evaluation - Language Tag Cardinality (1)}
		\label{tab:thesauri-evaluation-language-tag-cardinality-1}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccc@{}}
           & \multicolumn{4}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-5}
    \\       \textbf{Language Tag Cardinality}
					 & \emph{\rot{EARTh}}
					 & \emph{\rot{GEMET}}
					 & \emph{\rot{EuroVoc}}
					 & \emph{\rot{SLD}}
    \\ \midrule
		\emph{LANGUAGE-TAG-CARDINALITY-01}\textsuperscript{**} & \ding{55} & 2,318,895 & \ding{55} & 30,781 \\
		\emph{LANGUAGE-TAG-CARDINALITY-02}\textsuperscript{*} & \ding{55} & \ding{55} & \ding{55} & \ding{55} \\
		\emph{LANGUAGE-TAG-CARDINALITY-03}\textsuperscript{*} & 224,206 & \ding{55} & \ding{55} & 31,195 \\
		\emph{LANGUAGE-TAG-CARDINALITY-04}\textsuperscript{*} & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ \\
    \bottomrule
    \end{tabular}
    \caption{Thesauri Evaluation - Language Tag Cardinality (2)}
		\label{tab:thesauri-evaluation-language-tag-cardinality-2}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccccccccccc@{}}
           & \multicolumn{12}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-13}
    \\       \textbf{Constraints}
           & \emph{\rot{TheSoz}}
           & \emph{\rot{STW}}
           & \emph{\rot{AGROVOC}}
					 & \emph{\rot{TGN}}
           & \emph{\rot{UNESCO}}
					 & \emph{\rot{ODT}}
					 & \emph{\rot{SSWT}}
					 & \emph{\rot{GBA-GU}}
					 & \emph{\rot{GBA-GTS}}
					 & \emph{\rot{GBA-L}}
					 & \emph{\rot{GBA-LU}}
					 & \emph{\rot{CECCT}}
    \\ \midrule
		\emph{PROPERTY-DOMAIN-01 (!)}\textsuperscript{***} &  &  &  &  &  & \\
		\emph{PROPERTY-RANGES-01 (!)}\textsuperscript{***} &  &  &  &  &  & \\
		\emph{DISJOINT-PROPERTIES-01 (!)}\textsuperscript{***} &  &  &  &  &  & \\
		\emph{DISJOINT-PROPERTIES-02 (!)}\textsuperscript{***} &  &  &  &  &  & \\
		\emph{DISJOINT-CLASSES-01 (!)}\textsuperscript{***} &  &  &  &  &  & \\
		\emph{EQUIVALENT-PROPERTIES-01 (!)}\textsuperscript{*} &  &  &  &  &  & \\
		\emph{UNIVERSAL-QUANTIFICATIONS-01 (!)}\textsuperscript{***} &  &  &  &  &  & \\
		\emph{CONTEXT-SPECIFIC-VALID-CLASSES-01 (!)}\textsuperscript{*} &  &  &  &  &  & \\
		\emph{CONTEXT-SPECIFIC-VALID-PROPERTIES-01 (!)}\textsuperscript{*} &  &  &  &  &  & \\
		\emph{RECOMMENDED-PROPERTIES-01 (!)}\textsuperscript{*} &  &  &  &  &  & \\
		\emph{VOCABULARY-01 (!)}\textsuperscript{***} &  &  &  &  &  & \\
		\emph{HTTP-URI-SCHEME-VIOLATION (!)}\textsuperscript{***} \\
    \bottomrule
    \end{tabular}
    \caption{Thesauri Evaluation - Constraints (1)}
		\label{tab:thesauri-evaluation-constraints-1}
    \end{center}
\end{table}

\begin{table}[H]
    \begin{center}
    \begin{tabular}{@{}lcccc@{}}
           & \multicolumn{4}{c}{\textbf{Data Sets}}
    \\  \cmidrule{2-5}
    \\       \textbf{Constraints}
					 & \emph{\rot{EARTh}}
					 & \emph{\rot{GEMET}}
					 & \emph{\rot{EuroVoc}}
					 & \emph{\rot{SLD}}
    \\ \midrule
		\emph{PROPERTY-DOMAIN-01 (!)}\textsuperscript{***}\\
		\emph{PROPERTY-RANGES-01 (!)}\textsuperscript{***}\\
		\emph{DISJOINT-PROPERTIES-01 (!)}\textsuperscript{***}\\
		\emph{DISJOINT-PROPERTIES-02 (!)}\textsuperscript{***}\\
		\emph{DISJOINT-CLASSES-01 (!)}\textsuperscript{***}\\
		\emph{EQUIVALENT-PROPERTIES-01 (!)}\textsuperscript{*}\\
		\emph{UNIVERSAL-QUANTIFICATIONS-01 (!)}\textsuperscript{***}\\
		\emph{CONTEXT-SPECIFIC-VALID-CLASSES-01 (!)}\textsuperscript{*} \\
		\emph{CONTEXT-SPECIFIC-VALID-PROPERTIES-01 (!)}\textsuperscript{*} \\
		\emph{RECOMMENDED-PROPERTIES-01 (!)}\textsuperscript{*} \\
		\emph{VOCABULARY-01 (!)}\textsuperscript{***} \\
		\emph{HTTP-URI-SCHEME-VIOLATION (!)}\textsuperscript{***} \\
    \bottomrule
    \end{tabular}
    \caption{Thesauri Evaluation - Constraints (2)}
		\label{tab:thesauri-evaluation-constraints-2}
    \end{center}
\end{table}

\section{Evaluation of Rectangular Data (\emph{PHDD})}

In this section, the quality of rectangular (\emph{PHDD}) data sets is evaluated by validating appropriate RDF constraints assigned to several RDF constraint types.
First, we show the results of the evaluation of diverse data sets, then we give an overview over the evaluated data sets, and finally we provide details about the evaluation.

\subsection{Evaluation Results}

\subsection{Data Sets Overview}

\subsection{Detailed Evaluation}

In this sub section, we give details about the evaluation in form of diverse tables containing the number of constraint violations per evaluated data set and constraint of particular constraint types.

\section{Evaluation of Statistical Classifications (\emph{XKOS})}

In this section, the quality of the metadata on statistical classifications (\emph{XKOS}) data sets is evaluated by validating appropriate RDF constraints assigned to several RDF constraint types.
First, we show the results of the evaluation of diverse data sets, then we give an overview over the evaluated data sets, and finally we provide details about the evaluation.

\subsection{Evaluation Results}

\subsection{Data Sets Overview}

\begin{table}[H]
	\centering
		\begin{tabular}{l|l}
      \textbf{Abbr.} & \textbf{Statistical Classifications} \\		
      \hline
    \emph{NAF} & \emph{Nomenclature d'activités française}\tablefootnote{\url{http://rdf.insee.fr/codes/index.html}} \\
		\emph{PCS} & \emph{Nomenclature des Professions et Catégories Socioprofessionnelles}\tablefootnote{\url{http://rdf.insee.fr/codes/index.html}} \\
		\emph{CJ} & \emph{Nomenclature des catégories juridiques}\tablefootnote{\url{http://rdf.insee.fr/codes/index.html}} \\
		\emph{ISIC} & \\
		\emph{ISCO} & \\
		\end{tabular}
	\caption{Statistical Classifications Abbreviations}
	\label{tab:statistical-classifications-abbreviations}
\end{table}

\emph{Nomenclature d'activités française (NAF)} is the French refinement of the \emph{NACE} classification expressed in XKOS having explanatory notes.
\emph{Nomenclature des Professions et Catégories Socioprofessionnelles (PCS)} and \emph{Nomenclature des catégories juridiques (CJ)} are French classifications expressed in XKOS.
The statistical classification \emph{ISIC} has explanatory notes too. 

%\begin{table}[H]
    %\begin{center}
    %\begin{tabular}{@{}lccccccccccc@{}}
           %& \multicolumn{6}{c}{\textbf{Counts}}
    %\\  \cmidrule{2-7}
    %\\       \textbf{Data Sets}
           %& \textbf{\rot{triples}}
           %& \textbf{\rot{}}
           %& \textbf{\rot{}}
           %& \textbf{\rot{}}
           %& \textbf{\rot{}}
					 %& \textbf{\rot{}}
					 %& \textbf{\rot{}}
    %\\ \midrule
    %\emph{NAF} &  &  &  &  &  & \\
		%\emph{PCS} &  &  &  &  &  & \\
		%\emph{CJ} &  &  &  &  &  & \\
		%\emph{ISIC} &  &  &  &  &  & \\
		%\emph{ISCO} &  &  &  &  &  & \\
		%\hline
		%\textbf{Total} & & & & & & \\
    %\bottomrule
    %\end{tabular}
    %\caption{Statistical Classifications Overview}
		%\label{tab:statistical-classifications-overview}
    %\end{center}
%\end{table}

\subsection{Detailed Evaluation}

In this sub section, we give details about the evaluation in form of diverse tables containing the number of constraint violations per evaluated data set and constraint of particular constraint types.

\section{Related Work}

The data most often used in research within the SBE community is \emph{person-level data}, i.e. data collected about individuals, businesses, and households in form of responses to studies or taken from administrative registers
(such as hospital records, registers of births and deaths). 
The range of person-level data covers many different domains and is very broad - 
including census, education, and health data as well as all types of business, social, and labor force surveys.  
Increasingly, this type of research data is
held within data archives or data libraries after it has been collected, so that it may be
reused by future researchers. 
In performing their research, the detailed person-level
data is aggregated into less confidential multi-dimensional tables which answer particular research questions.
Portals harvest metadata (as well as publicly available data) from multiple data providers in form of RDF.
To ensure high quality, the metadata must satisfy certain criteria - specified in terms of RDF constraints.  
After validating the metadata according to these constraints, portals offer added values to their customers, e.g. by searching over and comparing metadata of multiple providers. 

By its nature, person-level data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
The purpose of publicly available aggregated data, on the other hand, is to get a first overview and to gain an interest in further analyses on the underlying person-level data.
Researchers typically represent their results as aggregated data in form of two-dimensional tables with only a few columns (so-called \emph{variables} such as \emph{sex} or \emph{age}).
The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e. multi-dimensional aggregate data, in RDF \cite{Cyganiak2010}. 
Aggregate data is derived from person-level data by statistics on groups or aggregates such as counts, means, and frequencies.
The SDMX metadata standard – used as the basis for \emph{QB} – and DDI have traditionally made efforts to align their content. 
Similarly, some of the developers of \emph{Disco} were also involved in the development of \emph{QB}, 
allowing the RDF versions of these standards to retain that alignment.
While \emph{Disco} and \emph{QB} provide terms for the description of data sets, 
both on a different level of aggregation, 
the \emph{Data Catalog Vocabulary (DCAT)}\footnote{\url{http://www.w3.org/TR/vocab-dcat/}} enables the representation of these data sets inside of data collections like repositories, catalogs, or archives. 
The relationship between data collections and their contained data sets is useful, since such collections are a typical entry point when searching for data.
Although, in most cases aggregated data is still published in form of PDFs, 
it is more and more common to publish aggregated data as CSV files,
allowing to perform first calculations (either using all variables or only a subset).
%For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
In 2014, SBE and Linked Data community members developed the \emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} vocabulary to represent aggregated and person-level data in a rectangular format. 
The data could be either represented in records with character-separated values (CSV) or in records with fixed length. 

For more detailed analyses, researchers refer to person-level data from which aggregated data is derived from, 
as person-level data include additional variables needed for further research.
%Although not that common, the other direction is also possible, 
%i.e. researchers may use metadata on person-level data to search for aggregated data.
One very common example for detailed analyses on person-level data is the content-driven comparison of multiple studies.
Researchers get promising findings (in form of published tables with a few columns) within a metadata portal leading to subsequent research questions 
like 'How to compare the unemployment rate of different countries (e.g. Germany, UK, and France) in the last 10 years grouped by age?'.
The first step is to determine in which countries the unemployment rate is collected and which other variables of each country-specific study are theoretically comparable and can therefore be used to answer the underlying research question.
A \emph{study} represents the process by which a data set was generated or collected.
Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger}, or by a code list including multiple age clusters (such as '0 to 10' and '11 to 20'). 
To determine if variables measuring \emph{age} 
- collected within multiple studies of different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
are comparable, both content-driven and technology-driven validation is performed.
An example for a content-driven validation is to investigate if variables are represented in a compatible way,
i.e. are the variables' code lists theoretically comparable.
Technically, it can be validated (1) if variable definitions are available, (2) if code lists are properly structured, and (3) if for each code an associated category (a human-readable label) is specified.

Data providers and harvesters do not only offer metadata but also publicly available data on different level of detail.
To ensure high data quality and trust, they have to analyze and validate the data (are fundamental data fragments available?, how does valid data look like?). 
%They validate, e.g., if fundamental data parts are available and define how valid data should look like (using syntactic rules).
Provenance (where does the data come from?) is an important aspect in evaluating data quality.
As data searchers know exactly which data sources they trust and which are reasonable to meet their individual use cases, 
RDF data validation can only be performed semi-automatically, i.e., an automatic approach serves as basis for intellectual decisions. 

\section{Conclusion and Future Work}

We implemented a validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages and to ensure correct syntax, semantics, and integrity of diverse vocabularies such as \emph{Disco, QB, PHDD, SKOS, and XKOS}.
We exhaustively evaluated the metadata quality of large real world aggregated data sets (\emph{QB}), person-level data sets (\emph{Disco}), thesauri (\emph{SKOS}), statistical classifications (\emph{XKOS}), and rectangular data sets (\emph{PHDD}) by means of 212 $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
In total, we validated more than 4.2 billion triples and 15 thousand data sets.

\bibliography{../../literature/literature}{}
\bibliographystyle{plain}
\setcounter{tocdepth}{1}
%\listoftodos
\end{document}
